---
title: "LMT time series July 20-Aug 17 2020"
author: "Janis Corona"
date: "8/19/2020"
output: html_document
---



```{r}
library(dplyr)
library(lubridate)
```


```{r}
lmt1 <- read.csv('LMT-7-20-2020.csv',sep=',',header=F,
                 na.strings=c('',' ','NA'),stringsAsFactors = F)

lmt2 <- read.csv('LMT-7-27-2020.csv',sep=',',header=F,
                 na.strings=c('',' ','NA'),stringsAsFactors = F)
lmt3 <- read.csv('LMT-8-3-2020.csv',sep=',',header=F,
                 na.strings=c('',' ','NA'),stringsAsFactors = F)
lmt4 <- read.csv('LMT-8-10-2020.csv',sep=',',header=F,
                 na.strings=c('',' ','NA'),stringsAsFactors = F)
lmt5 <- read.csv('LMT-8-17-2020.csv',sep=',',header=F,
                 na.strings=c('',' ','NA'),stringsAsFactors = F)

header <- read.csv('tableJobsHeader.csv')
```


```{r}
colnames(lmt1) <- header$x
colnames(lmt2) <- header$x
colnames(lmt3) <- header$x
colnames(lmt4) <- header$x
colnames(lmt5) <- header$x

lmt1$state <- toupper(lmt1$state)
lmt2$state <- toupper(lmt2$state)
lmt3$state <- toupper(lmt3$state)
lmt4$state <- toupper(lmt4$state)
lmt5$state <- toupper(lmt5$state)

```


```{r}
unique(lmt1$date_daysAgo)
```


```{r}
lmt1$date_daysAgo <- gsub('Just posted',0,lmt1$date_daysAgo)
lmt1$date_daysAgo <- gsub('Today',0,lmt1$date_daysAgo)

lmt2$date_daysAgo <- gsub('Just posted',0,lmt2$date_daysAgo)
lmt2$date_daysAgo <- gsub('Today',0,lmt2$date_daysAgo)

lmt3$date_daysAgo <- gsub('Just posted',0,lmt3$date_daysAgo)
lmt3$date_daysAgo <- gsub('Today',0,lmt3$date_daysAgo)

lmt4$date_daysAgo <- gsub('Just posted',0,lmt4$date_daysAgo)
lmt4$date_daysAgo <- gsub('Today',0,lmt4$date_daysAgo)

lmt5$date_daysAgo <- gsub('Just posted',0,lmt5$date_daysAgo)
lmt5$date_daysAgo <- gsub('Today',0,lmt5$date_daysAgo)


```


```{r}
lmt1$date_daysAgo <- as.numeric(paste(lmt1$date_daysAgo))
lmt2$date_daysAgo <- as.numeric(paste(lmt2$date_daysAgo))
lmt3$date_daysAgo <- as.numeric(paste(lmt3$date_daysAgo))
lmt4$date_daysAgo <- as.numeric(paste(lmt4$date_daysAgo))
lmt5$date_daysAgo <- as.numeric(paste(lmt5$date_daysAgo))

```


```{r}
lmt1s <- strsplit(lmt1$todaysDate,split=' ')
lmt1$wday <- as.character(lapply(lmt1s,'[',1))
lmt1$month   <- as.character(lapply(lmt1s,'[',2))
lmt1$dayMonth <- as.character(lapply(lmt1s, '[',3))
lmt1$timeHMS  <- as.character(lapply(lmt1s,'[',4))
lmt1$year <- as.character(lapply(lmt1s,'[',5))

lmt2s <- strsplit(lmt2$todaysDate,split=' ')
lmt2$wday <- as.character(lapply(lmt2s,'[',1))
lmt2$month   <- as.character(lapply(lmt2s,'[',2))
lmt2$dayMonth <- as.character(lapply(lmt2s, '[',3))
lmt2$timeHMS  <- as.character(lapply(lmt2s,'[',4))
lmt2$year <- as.character(lapply(lmt2s,'[',5))

lmt3s <- strsplit(lmt3$todaysDate,split=' ')
lmt3$wday <- as.character(lapply(lmt3s,'[',1))
lmt3$month   <- as.character(lapply(lmt3s,'[',2))
lmt3$dayMonth <- as.character(lapply(lmt3s, '[',3))
lmt3$timeHMS  <- as.character(lapply(lmt3s,'[',4))
lmt3$year <- as.character(lapply(lmt3s,'[',5))

lmt4s <- strsplit(lmt4$todaysDate,split=' ')
lmt4$wday <- as.character(lapply(lmt4s,'[',1))
lmt4$month   <- as.character(lapply(lmt4s,'[',2))
lmt4$dayMonth <- as.character(lapply(lmt4s, '[',3))
lmt4$timeHMS  <- as.character(lapply(lmt4s,'[',4))
lmt4$year <- as.character(lapply(lmt4s,'[',5))

lmt5s <- strsplit(lmt5$todaysDate,split=' ')
lmt5$wday <- as.character(lapply(lmt5s,'[',1))
lmt5$month   <- as.character(lapply(lmt5s,'[',2))
lmt5$dayMonth <- as.character(lapply(lmt5s, '[',3))
lmt5$timeHMS  <- as.character(lapply(lmt5s,'[',4))
lmt5$year <- as.character(lapply(lmt5s,'[',5))

```


```{r}
JulAug <- rbind(lmt1,lmt2,lmt3,lmt4,lmt5)

```


```{r}
JulAug$nMonth <- ifelse(JulAug$month=='Jan',1,
                  ifelse(JulAug$month=='Feb',2,
                  ifelse(JulAug$month=='Mar',3,
                  ifelse(JulAug$month=='Apr',4,
                  ifelse(JulAug$month=='May',5,
                  ifelse(JulAug$month=='Jun',6,
                  ifelse(JulAug$month=='Jul',7,
                  ifelse(JulAug$month=='Aug',8,
                  ifelse(JulAug$month=='Sep',9,
                  ifelse(JulAug$month=='Oct',10,
                  ifelse(JulAug$month=='Nov',11,
                  ifelse(JulAug$month=='Dec',12,NA))))))))))))
```


```{r}
JulAug$mdy <- paste(JulAug$nMonth,JulAug$dayMonth,JulAug$year,sep='/')
```


```{r}
JulAug$mdy <- mdy(JulAug$mdy)
JulAug$jobPosted_nDays_ago <- JulAug$mdy-JulAug$date_daysAgo
```


```{r}
JulAugNot30 <- subset(JulAug, JulAug$date_daysAgo != 30)
JulAugNot30 <- JulAugNot30[!duplicated(JulAugNot30),]
```


```{r}
jobsPerStateCityDayPosted <- JulAugNot30 %>% 
  group_by(state,city,jobPosted_nDays_ago) %>% count(jobPosted_nDays_ago)

```


```{r}
colnames(jobsPerStateCityDayPosted)[3:4] <- c('datePosted','LMT_jobsPosted')
```


```{r}
write.csv(JulAugNot30,'JulAugNot30.csv',row.names=F)
write.csv(jobsPerStateCityDayPosted,'LMT_jobsPostedDateCityState.csv',
          row.names=F)
```

***


Lets read in the available information on nannys, nurses (Aug 3, 2020 missed getting pulled from web that week), personal assistants, security, and warehouse jobs available in the US.
```{r}

nannyListings <- read.csv(
  './alternate jobs/nanny_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)

#reread in the file if starting at ***
lmtListings <- read.csv(
  'LMT_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)

nurseListings <- read.csv(
  './alternate jobs/nurse_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)

personalAssistantListings <- read.csv(
  './alternate jobs/personalAssistant_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)

securityListings <- read.csv(
  './alternate jobs/security_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)

warehouseListings <- read.csv(
  './alternate jobs/warehouse_jobsPostedDateCityState.csv',
                          sep=',',header=T, na.strings=c('',' ','NA'),
                          stringsAsFactors = T)


```


```{r}
colnames(lmtListings)[4] <- 'jobsPosted'
lmtListings$job <- 'LMT'

colnames(nannyListings)[4] <- 'jobsPosted'
nannyListings$job <- 'nanny'

colnames(nurseListings)[4] <- 'jobsPosted'
nurseListings$job <- 'nurse'

colnames(personalAssistantListings)[4] <- 'jobsPosted'
personalAssistantListings$job <- 'personal assistant'

colnames(securityListings)[4] <- 'jobsPosted'
securityListings$job <- 'security'

colnames(warehouseListings)[4] <- 'jobsPosted'
warehouseListings$job <- 'warehouse'


```

```{r}
allJobPostings <- rbind(lmtListings,nannyListings,
                        nurseListings, personalAssistantListings,
                        securityListings,warehouseListings)
allJobPostings$job <- as.factor(paste(allJobPostings$job))
```


```{r}
write.csv(allJobPostings,'allJobsPosted.csv',row.names=F)
```

***
Lets get data that also gets the average hourly and annual salary for each city by reading in that data.
```{r}
wages <- read.csv('JulAugNot30.csv',sep=',',header=T,
                  na.strings=c('',' ','NA'),stringsAsFactors = T)
```


```{r}
colnames(wages)
```


```{r}
cityWages <- wages %>% group_by(state,city,jobSearched,
                                jobPosted_nDays_ago) %>% summarise_at(vars(MinHourlySalary,MaxHourlySalary,MinAnnualSalary,
                                                                                      MaxAnnualSalary),mean)
```


```{r}
write.csv(cityWages,'LMT_citywages.csv',row.names=F)
```


Lets import all of the city wage data for our five selected jobs.
```{r}
lmtCityWages <- read.csv('LMT_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)
```


```{r}
nannyCityWages <- read.csv('./alternate jobs/nanny_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)

nurseCityWages <- read.csv('./alternate jobs/nurse_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)

personalAssistantCityWages <- read.csv('./alternate jobs/personalAssistant_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)

securityCityWages <- read.csv('./alternate jobs/security_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)

warehouseCityWages <- read.csv('./alternate jobs/warehouse_citywages.csv',sep=',',header=T,
                         na.strings=c('',' ','NA'),
                         stringsAsFactors = F)

```


Lets combine all this data into one table. 
```{r}
BigDataWages <- rbind(lmtCityWages,
                      nannyCityWages,
                      nurseCityWages,
                      personalAssistantCityWages,
                      securityCityWages,
                      warehouseCityWages)
colnames(BigDataWages)[4] <- 'dateJobPosted'
```


```{r}
write.csv(BigDataWages,'BigDataWages.csv', row.names=F)
```


```{r}

```

