---
title: "number of businesses each state"
author: "Janis Corona"
date: "8/12/2020"
output: html_document
---

This function will do similar to the other function that scrapes Indeed for job searched, city, and state, but instead with yellowpages.com.It will append the retrieved data to a table, for the data on advertised pay if available for a job title, city, and state searched in Indeed with this function, the rvest webscrape package and the selector gadget, https://selectorgadget.com/ , the chrome extension for highlighting html and getting the tag location. 

Create a directory named with the business type your looking for, like massage, chiropractor, gym, etc.
```{r}
BUSINESS <- 'jail or prison'
Business_Path <- './jail or prison'
```


```{r}
#Loading the rvest package
library(rvest)
library(lubridate)
library(dplyr)
```


```{r}
if (dir.exists(Business_Path)){
  unlink(Business_Path, recursive=TRUE)
  dir.create(Business_Path)
} else {
  dir.create(Business_Path)
}

```

This funciton won't return the tables to look at, but will write all results to a csv file to read in when done importing the 150 cities of the three most populated city in each US state other than the newly added District of Columbia.
```{r}

writeYellowPageBusinessTypes <- function(businessCityState){
  url <- 'https://www.yellowpages.com/search?search_terms=businessType&geo_location_terms=CityName%2C+stateAbb'
  url2 <- 'https://www.yellowpages.com/search?search_terms=businessType&geo_location_terms=CityName%2C%20stateAbb&page=2'
  url3 <- 'https://www.yellowpages.com/search?search_terms=businessType&geo_location_terms=CityName%2C%20stateAbb&page=3'
  url4 <- 'https://www.yellowpages.com/search?search_terms=businessType&geo_location_terms=CityName%2C%20stateAbb&page=4'
  url5 <- 'https://www.yellowpages.com/search?search_terms=businessType&geo_location_terms=CityName%2C%20stateAbb&page=5'
  
  inputs <- strsplit(businessCityState, split=',')
  
  businessType <- lapply(inputs, '[', 1)
  business <- as.character(businessType)
  business <- trimws(business, which='left', whitespace='[\t\r\n]')
  business <- trimws(business, which='right',whitespace='[\t\r\n]')
  businessOne <- gsub(' ','+',business)
  businessPlus <- gsub(' ','%20',business)
  
  cityName <- lapply(inputs,'[',2)
  cityName <- as.character(cityName)
  cityName <- trimws(cityName, which='left',whitespace='[\t\r\n]')
  cityName <- trimws(cityName, which='right',whitespace='[\t\r\n]')
  city <- cityName
  cityOne <- gsub(' ','+',city)
  cityPlus <- gsub(' ','%20',city)
  
  stateAbb <- lapply(inputs, '[',3)
  stateAbb <- as.character(stateAbb)
  stateAbb <- trimws(stateAbb, which='left', whitespace='[\t\r\n]')
  stateAbb <- trimws(stateAbb, which='right',whitespace='[\t\r\n]')
  state <- stateAbb
  
  url <- gsub('businessType',businessOne, url)
  url <- gsub('CityName',cityOne, url)
  url <- gsub('stateAbb',state, url)
  
  url2 <- gsub('businessType',businessPlus, url2)
  url2 <- gsub('CityName',cityPlus, url2)
  url2 <- gsub('stateAbb',state, url2)
  
  url3 <- gsub('businessType',businessPlus, url3)
  url3 <- gsub('CityName',cityPlus, url3)
  url3 <- gsub('stateAbb',state, url3)

  url4 <- gsub('businessType',businessPlus, url4)
  url4 <- gsub('CityName',cityPlus, url4)
  url4 <- gsub('stateAbb',state, url4)

  url5 <- gsub('businessType',businessPlus, url5)
  url5 <- gsub('CityName',cityPlus, url5)
  url5 <- gsub('stateAbb',state, url5)

  webpage <- read_html(url)
  webpage2 <- read_html(url2)
  webpage3 <- read_html(url3)
  webpage4 <- read_html(url4)
  webpage5 <- read_html(url5)
  
  business_html <- html_nodes(webpage,'h2.n:nth-child(1)')
  business1 <- html_text(business_html)
  
  business_html2 <- html_nodes(webpage2,'h2.n:nth-child(1)')
  business2 <- html_text(business_html2)

  business_html3 <- html_nodes(webpage3,'h2.n:nth-child(1)')
  business3 <- html_text(business_html3)

  business_html4 <- html_nodes(webpage4,'h2.n:nth-child(1)')
  business4 <- html_text(business_html4)

  business_html5 <- html_nodes(webpage5,'h2.n:nth-child(1)')
  business5 <- html_text(business_html5)

  Business <- as.data.frame(c(business1,business2, business3, business4, business5))
  colnames(Business) <- 'businessType'
  Business$businessType <- as.character(paste(Business$businessType))
  Business$businessType <- gsub('\n','',Business$businessType)


  cityDF <- as.data.frame(rep(cityName,length(Business$businessType)))
  colnames(cityDF) <- "city"
  
  stateDF <- as.data.frame(rep(state,length(Business$businessType)))
  colnames(stateDF) <- 'state'
  
  businessSearchDF <- as.data.frame(rep(Business$businessType,
                                        length(Business$businessType)))
  colnames(businessSearchDF) <- 'businessType'
  
  date <- as.data.frame(rep(date(),length(Business$businessType)))
  colnames(date) <- 'todaysDate'
  
  tableBusinesses <- cbind(cityDF,stateDF,businessSearchDF,date)
  
  setwd(Business_Path)
  
  business2 <- gsub(' ','-',business)
  city2 <- gsub(' ','-',cityName)
  
  write.csv(tableBusinesses,paste(business2,city2,state,".csv",sep='_'),row.names = FALSE)
  write.table(tableBusinesses, 
              paste(businessType,".csv",sep=''), append=TRUE,
              col.names=FALSE, sep=",", quote=TRUE,qmethod="double",
              row.names=FALSE)
  names <- colnames(tableBusinesses)
  write.csv(names,paste('tableBusinessesHeader_',businessType,'.csv',sep=''),row.names=FALSE)
  
  setwd('../')
  return(list(dim(tableBusinesses),tail(tableBusinesses,2)))
}
```

***

table10cities-altered.csv and read it in.
```{r}
table10 <- read.csv('../table10cities-altered.csv',sep=',', header=TRUE, na.strings=c('',' ','NA'))
```

```{r}
head(table10)
```

```{r}
Table10 <- table10[,c(2,4)]
Table10$businessType <- BUSINESS
Table10$functionInput <- paste(Table10$businessType,Table10$topCity,
                               Table10$stateAbbreviations, sep=',')
Table10$functionInput <- as.character(Table10$functionInput)
head(Table10)
```

```{r}
for (i in Table10$functionInput[1:22]){
  writeYellowPageBusinessTypes(i)
  
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')

}
```


```{r}
for (i in Table10$functionInput[23:50]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[51:75]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[76:114]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[115:150]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[151:200]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[201:244]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```





```{r}
for (i in Table10$functionInput[245:275]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[276:300]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[301:325]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[326:350]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[351:375]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[376:400]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[401:425]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[426:450]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[451:477]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```


```{r}
for (i in Table10$functionInput[479:500]){
  writeYellowPageBusinessTypes(i)
    
  bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

  header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
  BizCities <- bizCities[!duplicated(bizCities),]
  colnames(BizCities) <- header$x
  colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')


}
```




***


***



Group by state, and get the count of businesses in each state.
```{r}

bizCities <- read.csv(paste(Business_Path,'/',BUSINESS,'.csv',sep=''), sep=",", 
                        header=FALSE, na.strings=c('',' ','NA'))

header <- read.csv(paste(Business_Path,'/tableBusinessesHeader_',BUSINESS,'.csv',
                         sep=''), sep=',')
BizCities <- bizCities[!duplicated(bizCities),]
colnames(BizCities) <- header$x
colnames(BizCities)[3] <- paste(BUSINESS,colnames(BizCities)[3],sep='_')

BizCities$state <- as.factor(BizCities$state)

businessCounts <- BizCities %>% group_by(state) %>% count(state)
colnames(businessCounts)[2] <- paste(BUSINESS,'businessListings',sep='_')
businessCounts
```


```{r}
write.csv(businessCounts,paste('statesRates-',BUSINESS,'.csv'), row.names=FALSE)
```

